Title of Paper

### 2017-02-14 paper.tex
refine intro

Single Instruction, Multiple-Data (SIMD) processing, also known as vector-processing, is an important parallel computing paradigm that is increasingly being used in scientific computing.
While central processing unit (CPU) clock speeds have increased rapidly over the past few decades---the phenomena known as Moore's Law---power consumption and head dissipation issues have caused this trend to slow.
Traditional multi-core parallelism is often used to increase CPU performance, however SIMD processors---and the related Single Instruction, Multiple Thread (SIMT) processors, e.g. graphics processing units (GPUs)---have become more popular due to their increased floating operation throughput.
The parallel programming standard OpenCL~\cite{stone2010opencl} has further enabled adoption of vector-processing based codes in scientific computing by providing a common application program interface (API) for execution on heterogeneous systems (e.g. CPU, GPU, etc.).

@@

A SIMD instruction utilizes specialized vector processing hardware to execute the same floating point operation (e.g. multiplication, division, etc.) on multiple pieces of data concurrently (Fig.~\ref{F:SIMD}).
Nearly all modern CPUs have vector processing units capable of running SIMD instructions with typical vector widths of \SIrange{128}{256}{\bit}, e.g. the SSE or AVX2 instruction sets.
Additionally, specialized hardware accelerators, e.g. Intel's Xeon Phi co-processor (or MIC), have been developed that have tens of cores with very wide (\SIrange{256}{512}{\bit}) SIMD units---the AVX-512 instruction set---while forthcoming Intel CPUs (the Skylake Xeon and Cannon Lake architectures) are also expected to support AVX-512.
\todo[inline]{Find a source for this?  It all seems to be weird cpu journalism sites, maybe search intel}

>>>>

Single Instruction, Multiple-Data (SIMD) processing, also known as vector-processing, is an important parallel computing paradigm used increasingly in scientific computing.
While central processing unit (CPU) clock speeds have increased rapidly over the past few decades---the phenomena known as Moore's Law---power consumption and head dissipation issues have caused this trend to slow.
Traditional multi-core parallelism is often used to increase CPU performance, however SIMD processors---and the related Single Instruction, Multiple Thread (SIMT) processors, e.g. graphics processing units (GPUs)---have gained recognition due to their increased floating operation throughput.
The parallel programming standard OpenCL~\cite{stone2010opencl} has further enabled adoption of vector-processing based codes in scientific computing by providing a common application program interface (API) for execution on heterogeneous systems (e.g. CPU, GPU, etc.).

@@

A SIMD instruction utilizes specialized vector processing hardware to execute the same floating point operation (e.g. multiplication, division, etc.) on multiple pieces of data concurrently (Fig.~\ref{F:SIMD}).
Nearly all modern CPUs have vector processing units capable of running SIMD instructions, typically capable of handling 2--4 concurrent double precision operations---known as the vector width.
Additionally, specialized hardware accelerators, e.g. Intel's Xeon Phi co-processor (or MIC), have been developed that have tens of cores with very wide vector widths (e.g. 4--8 double precision operations); these very wide vector widths are also expected on forthcoming Intel CPUs (the Skylake Xeon and Cannon Lake architectures).
